Cirriculum vitae

### 2024-03-22 qmd/cv.qmd
commit for 3/22 morning

---
layout: page
title: "Cirriculum vitae"
execute:
  freeze: true  # never re-render during project render
engine: knitr 
resources:
  - "../Aboutme/jackson_strand_updated_cv.pdf"
cv:
  pdf: "../Aboutme/jackson_strand_updated_cv.pdf"
---

@@

<div class = "container">
  <!-- Button to download the file -->
  <a href="../Aboutme/jackson_strand_updated_cv.pdf" download="Jackson Strand CV">
    <button class="button">Download</button>
  </a>
</div>

>>>>

---
layout: page
title: "Cirriculum vitae"
execute:
  freeze: true  # never re-render during project render
engine: knitr 
resources:
  - "../Aboutme/Jackson_Strand_CV.pdf"
cv:
  pdf: "../Aboutme/Jackson_Strand_CV.pdf"
---

<!-- remember to print to pdf and don't save as pdf -->

@@

<div class = "container">
  <!-- Button to download the file -->
  <a href="../Aboutme/Jackson_Strand_CV.pdf" download="Jackson Strand CV">
    <button class="button">Download</button>
  </a>
</div>
